---
title: "Análise 2000 (censo não compatibilizado)"
author: "Thais Takeuchi"
date: "2024-08-31"
output: html_document
---
## Load packages
```{r load, include = FALSE}
### Remove selected objects
rm(list = ls())

### Load Packages (and install packages if needed)
load.lib <- c("data.table","foreign","stargazer","devtools","stringi", "srvyr", "survey","tidyverse","gtools", "remote","installr","microdadosBrasil","ggplot2","viridis","hrbrthemes","WDI","dplyr", "arrow", "readxl","rio","writexl","dineq", "basedosdados", "httr", "haven", "openxlsx", "fixest","car")

### Instaling and loading packages
install.lib <- load.lib[!load.lib %in% installed.packages()]
for(lib in install.lib) install.packages(lib,dependencies=TRUE)
sapply(load.lib, require, character=TRUE)
```

## Carrega base 2000 (DataZoom)
```{r carrega base 2000 (DataZoom)}
# cp2000_nc <- read_dta("E:/Thais/Tese_Mestrado/tese_bases/censo/base_stata_2000_sem_comp/censo_pessoas_2000_filtrado_nao_comp.dta")
# write_parquet(cp2000_nc, "E:/Thais/Tese_Mestrado/tese_bases/censo/base_stata_2000_sem_comp/censo_pessoas_2000_filtrado_nao_comp_1.parquet")
cp2000_nc <- arrow::read_parquet("E:/Thais/Tese_Mestrado/tese_bases/censo/base_stata_2000_sem_comp/censo_pessoas_2000_filtrado_nao_comp_1.parquet")
```

```{r carrega bases auxiliares}
### Cultural proxies----

## Home country divorce rate
# home_country_div_rate <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/home_country_div_rate/home_country_div_rate.xlsx")
home_country_div_rate_1 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/home_country_div_rate/home_country_div_rate_1.xlsx")

## Proportion: divorce is never justifiable
# never_just_div_1995_1998 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/div_never_just/never_just_div_1995_1998.xlsx")
# never_just_div_1999_2004 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/div_never_just/never_just_div_1999_2004.xlsx")
# never_just_div_2005_2009 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/div_never_just/never_just_div_2005_2009.xlsx")

#-------------------------------------------------------------------------------
### Country of Origin Variables, measured in the year 2000 except where otherwise noted (paper)----

## GDP per capita
gdp_pc <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/gdp_per_capita/gdp_pc.xlsx")

## Average Female Age at First Marriage
# age_f_first_marriage <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/age_first_marriage/female_age_first_marriage.xlsx")
age_ffm <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/age_first_marriage/wb_mean_age_first_marriage.xlsx")

## Total fertility rate
fertility_rate <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/fertility_rate/fertility_rate.xlsx")

## Remarriage rate

# ## Proportion: weekly  church attendance and catholics
# church_catholic_1995_1998 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/church/church_catholic_1995_1998.xlsx")
church_catholic_1999_2004 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/church/church_catholic_1999_2004.xlsx")
# church_catholic_2005_2009 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/church/church_catholic_2005_2009.xlsx")

##### ff2009 (idea)
## LFP 2000
lfp <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/lfp/lfp_final.xlsx")

```

## MANIPULAÇÕES
```{r renomeia}
cp2000_nc_copy <- copy(cp2000_nc)
cp2000_nc <- cp2000_nc |> rename(pais_nascim = v4210)
cp2000_nc_copy <- cp2000_nc_copy |> rename(pais_nascim = v4210)

setDT(cp2000_nc, cp2000_nc_copy)

cp2000_nc <- cp2000_nc_copy |>
  mutate(pais_nascim = case_when(
    pais_nascim == 30 ~ "Argentina",
    pais_nascim == 31 ~ "Bolivia",
    pais_nascim == 32 ~ "Canada",
    pais_nascim == 33 ~ "Chile",
    pais_nascim == 34 ~ "Colombia",
    pais_nascim == 35 ~ "Costa Rica",
    pais_nascim == 36 ~ "Cuba",
    pais_nascim == 37 ~ "Ecuador",
    pais_nascim == 38 ~ "United States",
    pais_nascim == 39 ~ "Guatemala",
    pais_nascim == 40 ~ "Guyana",
    pais_nascim == 41 ~ "French Guiana",
    pais_nascim == 42 ~ "Haiti",
    pais_nascim == 43 ~ "Honduras",
    pais_nascim == 44 ~ "Belize",
    pais_nascim == 45 ~ "Jamaica",
    pais_nascim == 46 ~ "Mexico",
    pais_nascim == 47 ~ "Nicaragua",
    pais_nascim == 48 ~ "Panama",
    pais_nascim == 49 ~ "Paraguay",
    pais_nascim == 50 ~ "Peru",
    pais_nascim == 51 ~ "Dominican Republic",
    pais_nascim == 52 ~ "El Salvador",
    pais_nascim == 53 ~ "Suriname",
    pais_nascim == 54 ~ "Uruguay",
    pais_nascim == 55 ~ "Venezuela",
    pais_nascim == 56 ~ "America - others",
    pais_nascim == 58 ~ "Germany",
    pais_nascim == 59 ~ "Austria",
    pais_nascim == 60 ~ "Belgium",
    pais_nascim == 61 ~ "Bulgaria",
    pais_nascim == 62 ~ "Denmark",
    pais_nascim == 63 ~ "Spain",
    pais_nascim == 64 ~ "Finland",
    pais_nascim == 65 ~ "France",
    pais_nascim == 66 ~ "United Kingdom",
    pais_nascim == 67 ~ "Greece",
    pais_nascim == 68 ~ "Netherlands",
    pais_nascim == 69 ~ "Hungary",
    pais_nascim == 70 ~ "Ireland",
    pais_nascim == 71 ~ "Italy",
    pais_nascim == 72 ~ "Yugoslavia",
    pais_nascim == 73 ~ "Norway",
    pais_nascim == 74 ~ "Poland",
    pais_nascim == 75 ~ "Portugal",
    pais_nascim == 76 ~ "Romania",
    pais_nascim == 77 ~ "Sweden",
    pais_nascim == 78 ~ "Switzerland",
    pais_nascim == 79 ~ "Czechoslovakia",
    pais_nascim == 80 ~ "Russian Federation",
    pais_nascim == 81 ~ "Europe - others",
    pais_nascim == 82 ~ "Angola",
    pais_nascim == 83 ~ "Egypt",
    pais_nascim == 84 ~ "Mozambique",
    pais_nascim == 85 ~ "Africa - others",
    pais_nascim == 86 ~ "China",
    pais_nascim == 87 ~ "Taiwan",
    pais_nascim == 88 ~ "Korea",
    pais_nascim == 89 ~ "India",
    pais_nascim == 90 ~ "Israel",
    pais_nascim == 91 ~ "Japan",
    pais_nascim == 92 ~ "Lebanon",
    pais_nascim == 93 ~ "Pakistan",
    pais_nascim == 94 ~ "Syria",
    pais_nascim == 95 ~ "Turkey",
    pais_nascim == 96 ~ "Asia - others",
    pais_nascim == 97 ~ "Australia",
    pais_nascim == 98 ~ "Oceania - others",
    pais_nascim == 99 ~ "No specification",
    TRUE ~ as.character(pais_nascim)
  ))
```

Para uma proxy do controle de filhos no domicílio vou considerar se o entrevistado tem o filho menor de idade e acrescentar esse controle na sample de mulheres.

```{r manipula 2}
# transform metropolitan area variable to a factor variable
cp2000_nc$v1004 <- as.factor(cp2000_nc$v1004)

# create columns
cp2000_nc <- cp2000_nc |>
  mutate(
    ano_nasc = ano - v4752,
    rm = ifelse(v1004 != 28, 1, 0), #metropolitan region
    imm = ifelse(((v0420 - ano_nasc <= 5) & rm == 1), 1, 0),
    imm_div = ifelse((imm == 1
                     & v0438 == 3), 1, 0),
  )

cp2000_nc <- cp2000_nc |> 
  filter(v0438 != 5) |> #drop singles
  filter(v0438 != 4)  #drop widows


cp2000_nc <- cp2000_nc |>
  mutate(
    imm_homem = ifelse(v0401 == 1
                       & imm == 1, 1, 0),
    imm_alf = ifelse(imm == 1 & (v0428 == 1), 1, 0), 
    imm_fund_completo = ifelse(imm == 1
                                 & (v0432 == 5 |v0432 == 3), 1, 0), 
    imm_em_completo = ifelse(imm == 1
                               & (v0432 == 6| v0432 == 4), 1, 0), 
    imm_superior_completo = ifelse(imm == 1
                             & (v0432 == 7 | v0432 == 8), 1, 0), 
    filho_menor = ifelse(v4654 <= 18, 1, 0),
    imm_mulher1filho = ifelse(imm == 1
                              & v0401 == 2
                              & (v0463 >= 1), 1, 0)
  )


cp2000_nc <- cp2000_nc |> rename(wage = v4513)

cp2000_nc <- cp2000_nc |> 
  mutate(
    annual_wage = wage * 12,
    log_wage = log(wage),
    wage_fem = ifelse(imm == 1 & v0401 == 2, wage * 12, 0), # annual salary for women, replace NA with 0
    log_wage_fem = log(ifelse(is.na(wage_fem), 0, wage_fem)), # replace NA with 0 before taking log
    wage_men = ifelse(imm == 1 & v0401 == 1, wage * 12, 0), # annual salary for men, replace NA with 0
    log_wage_men = log(ifelse(is.na(wage_men), 0, wage_men)) # replace NA with 0 before taking log
  )

```

### sum immigrants
```{r soma dados}
# numero de imigrantes na amostra
imm_base <- cp2000_nc |> filter(imm == 1)
sum(imm_base$P001)
```

### sum divorced immigrants
```{r soma dados2}
# numero de imigrantes divorciados
imm_div_base <- cp2000_nc |> filter(imm_div == 1)
sum(imm_div_base$P001)
```

### Merge census to cultural proxies
``` {r empilha bases}
# Gerar uma base de imigrantes
cp2000_nc_imm <- cp2000_nc |> filter(imm == 1)

# Copia da base de imigrantes
cp2000_nc_imm_copy <- cp2000_nc_imm

# setwd("E:/Thais/Tcp2000_nc_imm# setwd("E:/Thais/Tese_Mestrado/scripts_tese")
# save.image("bases_2000_2010.RData")

## Juntando as bases

# cp2000_nc_imm com home country divorce rate
cp2000_nc_imm_1 <- merge(cp2000_nc_imm, home_country_div_rate_1, by = "pais_nascim", all.x = TRUE)

# com gdp_pc: considerar ano 2000
gdp_pc_2000 <- gdp_pc |> filter(ano_gdp_pc == 2000)

cp2000_nc_imm_2 <- merge(cp2000_nc_imm_1, gdp_pc_2000, by = "pais_nascim", all.x = TRUE)

# com age_f_first_marriage
cp2000_nc_imm_3 <- merge(cp2000_nc_imm_2, age_ffm, by = "pais_nascim", all.x = TRUE)

# com fertility_rate
cp2000_nc_imm_4 <- merge(cp2000_nc_imm_3, fertility_rate, by = "pais_nascim", all.x = TRUE)

# com fem lfp
cp2000_nc_imm_4.1 <- merge(cp2000_nc_imm_4, lfp, by = "pais_nascim", all.x = TRUE)

# # com church variables
# ## 1995_1998
# cp2000_nc_imm_5 <- merge(cp2000_nc_imm_4, church_catholic_1995_1998, by = "pais_nascim", all.x = TRUE)
# ## 1999_2004
cp2000_nc_imm_4.2 <- merge(cp2000_nc_imm_4.1, church_catholic_1999_2004, by = "pais_nascim", all.x = TRUE)
# ## 2005_2009
# cp2000_nc_imm_7 <- merge(cp2000_nc_imm_6, church_catholic_2005_2009, by = "pais_nascim", all.x = TRUE)
# 
# # com divorce never justifiable
# ## 1995_1998
# cp2000_nc_imm_5 <- merge(cp2000_nc_imm_4, church_catholic_1995_1998, by = "pais_nascim", all.x = TRUE)
# ## 1999_2004
# cp2000_nc_imm_6 <- merge(cp2000_nc_imm_5, church_catholic_1999_2004, by = "pais_nascim", all.x = TRUE)
# ## 2005_2009
# cp2000_nc_imm_7 <- merge(cp2000_nc_imm_6, church_catholic_2005_2009, by = "pais_nascim", all.x = TRUE)

# Tirando outros paises (...-others e paises com NA)

cp2000_nc_imm_5 <- cp2000_nc_imm_4.2 |> 
  filter(!`pais_nascim` %in% c("Africa - others", "America - others", "Asia - others", "Czechoslovakia","Yugoslavia"))

# # Seleciona colunas na base
# cp2000_nc_imm_5 <- cp2000_nc_imm_5[, c("pais_nascim", "ano", "UF", "regiao", "munic", "id_dom", "ordem", "sexo", "idade","imm_idade", "raca", "religiao", "nacionalidade", "ano_fix_res", "alfabetizado", "curso_concl", "vive_conjuge", "rend_ocup_prin", "filhos_vivos", "peso_pess", "anos_estudoC", "teve_conjuge", "estado_conj", "rend_fam", "deflator", "conversor", "rend_ocup_prin_def", "rend_total_def", "rend_fam_def", "codmun", "ano_nasc", "imm5anos", "imm", "imm_div", "imm_homem", "imm_alf", "imm_fund_incompleto", "imm_em_incompleto","imm_em_completo", "imm_em_mais", "imm_mulher1filho", "n_married", "n_divorce", "year_n_divorce", "year_n_married", "hcdr", "ano_gdp_pc", "gdp_pc", "gdp_pc_in_100000", "ano_wb_age_f_first_marriage", "ffm_age", "age_group_fertility", "indic_fertility", "ano_fertility", "fertility_rate")]

cp2000_nc_imm_5 <- cp2000_nc_imm_5 |> rename(escolaridade = v0432)

# transforma escolaridade em continua
cp2000_nc_imm_5$escolaridade_cont <- as.numeric(cp2000_nc_imm_5$escolaridade)

# cp2000_nc_imm_5$escolaridade <- factor(cp2000_nc_imm_5$escolaridade,
#                                     levels = c(0, 1, 2, 3, 4, 5, 6, 7, 8, 9),
#                                     labels = c("Alfabetização de adultos",
#                                                "Antigo primário",
#                                                "Antigo ginásio",
#                                                "Antigo clássico, científico, etc",
#                                                "Ensino fundamental ou 1º grau",
#                                                "Ensino médio ou 2º grau",
#                                                "Superior - graduação",
#                                                "Mestrado ou doutorado",
#                                                "Nenhum",
#                                                "Branco"))

# idade ao quadrado
cp2000_nc_imm_5 <- cp2000_nc_imm_5 |>
  mutate(
    age_fem = if_else(v0401 == 2, v4752, NA_real_),
  ) |>
  mutate(
    age_squared = v4752^2
  )

# paises_para_remover <- c("Argentina", "Australia", "Bolivia", "Chile", "China", 
#                          "Colombia", "Costa Rica", "Cuba", "Dominican Republic", 
#                          "Ecuador", "Egypt", "El Salvador", "French Guiana", 
#                          "Greece", "Guatemala", "Guyana", "Honduras", "India", 
#                          "Japan", "Korea", "Lebanon", "Mexico", "Nicaragua", 
#                          "Pakistan", "Panama", "Paraguay", "Peru", "Suriname", 
#                          "Syria", "Turkey", "Uruguay", "Venezuela")
# 
# # Filtrando o DataFrame para remover os países com NA em hcdr
# cp2000_nc_imm_5 <- cp2000_nc_imm_5[!cp2000_nc_imm_5$pais_nascim %in% paises_para_remover, ]

# Remove na coluna pais_nascim com valores NA
cp2000_nc_imm_5 <- cp2000_nc_imm_5[!is.na(cp2000_nc_imm_5$pais_nascim), ]

# base_partial_nc <- as.data.frame(cp2000_nc_imm_5)
# write_xlsx(base_partial_nc, "E:/Thais/Tese_Mestrado/tese_bases/base_gerada/base_nc.xlsx")
# 
# base_partial_nc <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/base_gerada/base_nc.xlsx")


```
## Graph: number of immigrants on Census 
```{r number of immigrants total}
library(ggplot2)
country_counts <- cp2000_nc_imm_5 |>
  group_by(pais_nascim) |>
  summarize(total_weight = sum(P001, na.rm = TRUE)) |>
  arrange(desc(total_weight))
colnames(country_counts) <- c("Country", "Count")

ggplot(country_counts, aes(x = reorder(Country, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +  
  labs(title = "Number of Observations by Country", 
       x = "Country", 
       y = "Number of Observations") +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 5.5),   
    axis.text.x = element_text(size = 7),   
    plot.title = element_text(size = 7, hjust = 0.5), 
    plot.margin = margin(1, 1, 1, 1, "cm")  
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.03)))
```


## Graph: number of immigrants on Census with hcdr !=0
```{r number of immigrants with hcdr}
library(ggplot2)

country_counts_hcdr <- cp2000_nc_imm_5 |>
  filter(hcdr != 0) |>  
  group_by(pais_nascim) |>
  summarize(total_weight = sum(P001, na.rm = TRUE)) |>
  arrange(desc(total_weight))

colnames(country_counts_hcdr) <- c("Country", "Count")

ggplot(country_counts_hcdr, aes(x = reorder(Country, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +  
  labs(title = "Number of Observations by Country", 
       x = "Country", 
       y = "Number of Observations") +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 5.5),   
    axis.text.x = element_text(size = 7),   
    plot.title = element_text(size = 7, hjust = 0.5), 
    plot.margin = margin(1, 1, 1, 1, "cm")  
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.03)))
```

## FE Regressions

```{r reg1}
## Rodando a regressao (1) - table 2
# FE: idade
model1_nc <- feols(imm_div ~ hcdr + imm_homem + imm_fund_completo + imm_em_completo + imm_superior_completo | factor(v4752) + age_squared, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model1_nc)
```
*Pessoas mais velhas se divorciam menos, condicional à estarem casadas (Peters 1986). Como homens têm maior probabilidade de casarem novamente (Stevenson and Wolfers 2007), eles têm menor probabilidade de estarem divorciados do que as mulheres. Quanto maior a educação menor a probabilidade do divórcio ocorrer (Becker et al.1977;Isen and Stevenson 2010;Peters 1986)*

```{r reg2}
# FE: idade com escolaridade continua
model1_1_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont | factor(v4752) + age_squared, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model1_1_nc)
```
```{r reg3}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont | factor(v4752)+age_squared+v1004, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc)

```

```{r reg4}
# Drop Portugal (3)
base_partial_nc_sem_portugal <- cp2000_nc_imm_5 |>
  filter(pais_nascim != "Portugal")

model2_nc_sem_portugal <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont | factor(v4752)+age_squared+v1004, data = base_partial_nc_sem_portugal, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_sem_portugal)
```

```{r reg5}
# Drop Russia and Italy (4)
base_partial_nc_sem_russia_italy <- cp2000_nc_imm_5 |>
  filter(pais_nascim != "Russian Federation") |> 
  filter(pais_nascim != "Italy")

model2_nc_sem_russia_italy <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont | v4752+age_squared+v1004, data = base_partial_nc_sem_russia_italy, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_sem_portugal)

```
# Split sample

*We also separate the analysis by gender to test the hypothesis that women are more sensitive to divorce culture than men p.1016*

## Women

### With hcdr
```{r reg hcdr}
# Split sample: women
base_partial_nc_women <- cp2000_nc_imm_5 |>
  filter(v0401 == 2)

model2_nc_women4 <- feols(imm_div ~ hcdr, data = base_partial_nc_women, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_women4)

```

### With age dummy variables and msa fixed effects
```{r dummy and msa}
model2_nc_women5 <- feols(imm_div ~ hcdr + imm_fund_completo + imm_em_completo + imm_superior_completo | factor(v4752)+age_squared+v1004, data = base_partial_nc_women, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_women5)
```

### Plus age_children < 18

```{r reg women log(annual wage income) 6}
model2_nc_women6 <- feols(imm_div ~ hcdr + imm_fund_completo + imm_em_completo + imm_superior_completo + filho_menor| factor(v4752)+age_squared+v1004, data = base_partial_nc_women, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_women6)
```

### Plus log(annual wage income) and age_children < 18
```{r reg women log(annual wage income) 7}
model2_nc_women7 <- feols(imm_div ~ hcdr + imm_fund_completo + imm_em_completo + imm_superior_completo + log_wage_fem + filho_menor| factor(v4752)+age_squared+v1004, data = base_partial_nc_women, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_women7)
```

## Men
### Without age dummy variables and msa fixed effects

```{r reg7}
# Split sample: men
base_partial_nc_men <- cp2000_nc_imm_5 |>
  filter(v0401 == 1)

model2_nc_men1 <- feols(imm_div ~ hcdr + imm_fund_completo + imm_em_completo + imm_superior_completo, data = base_partial_nc_men, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_men1)
```

### With age dummy variables and msa fixed effects
```{r reg men}
# Split sample: men
model2_nc_men2 <- feols(imm_div ~ hcdr + imm_fund_completo + imm_em_completo + imm_superior_completo | factor(v4752)+age_squared+v1004, data = base_partial_nc_men, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_men2)
```

### With log(annual wage income)
```{r reg8}
# Split sample: men
model2_nc_men3 <- feols(imm_div ~ hcdr + imm_fund_completo + imm_em_completo + imm_superior_completo + log_wage_men| factor(v4752)+age_squared+v1004, data = base_partial_nc_men, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc_men3)
```

## Table 3: Home-country differences and the probability of being currently divorced (p.1026)

### with gdp_pc
```{r reg table 3.2}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont + gdp_pc_in_100000| factor(v4752)+age_squared+v1004, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc)

```

### with country-of-origin fertility rate
```{r reg table 3.3}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont + fertility_rate| factor(v4752)+age_squared+v1004, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc)

```

### with Country-of-Origin Proportion Weekly Church Attendance
```{r reg table 3.4}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont + tx_once_week_church_1999_2004| factor(v4752)+age_squared+v1004, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc)

```

### with Country-of-Origin Proportion Catholic (weird!)
```{r reg table 3.5}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont + tx_catholic_1999_2004| factor(v4752)+age_squared+v1004, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc)

```

### with Average female age at first marriage
```{r reg table 3.7}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont + ffm_age| factor(v4752)+age_squared+v1004, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc)

```

### with Everything! (not endogamy rate)
```{r reg table 3.8}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr +
                     imm_homem +
                     escolaridade_cont +
                     gdp_pc_in_100000 +
                     fertility_rate +
                     tx_once_week_church_1999_2004 +
                     tx_catholic_1999_2004 +
                     ffm_age |
                     factor(v4752)+age_squared+v1004, data = cp2000_nc_imm_5, weights = ~P001, cluster = ~pais_nascim)
summary(model2_nc)

```





