---
title: "Análise 1991"
author: "Thais Takeuchi"
date: "2024-08-31"
output: html_document
---

```{r setup, include = FALSE}
rm(list = (ls()))


### Load Packages (and install packages if needed)
load.lib <- c("data.table","foreign","stargazer","devtools","stringi", "srvyr", "survey","tidyverse","gtools", "remote","installr","microdadosBrasil","ggplot2","viridis","hrbrthemes","WDI","dplyr", "arrow", "readxl","rio","writexl","dineq", "basedosdados", "httr", "haven", "openxlsx", "fixest","car")

### Instaling and loading packages
install.lib <- load.lib[!load.lib %in% installed.packages()]
for(lib in install.lib) install.packages(lib,dependencies=TRUE)
sapply(load.lib, require, character=TRUE)
```

```{r}
## Country code mapping
country_code_mapping <- c(
  "Bolivia" = "BOL", "Peru" = "PER", "Germany" = "DEU", "Japan" = "JPN",
  "Paraguay" = "PRY", "Portugal" = "PRT", "Italy" = "ITA",
  "Spain" = "ESP", "India" = "IND", "United States" = "USA", "Colombia" = "COL",
  "Uruguay" = "URY", "Venezuela" = "VEN", "China" = "CHN", "Guyana" = "GUY",
  "France" = "FRA", "Argentina" = "ARG", "Chile" = "CHL", "Hungary" = "HUN",
  "Lebanon" = "LBN", "Austria" = "AUT", "Costa Rica" = "CRI",
  "Russian Federation" = "RUS", "Romania" = "ROU", "Turkey" = "TUR",
  "Czechoslovakia" = "CZE", "Poland" = "POL", "Cuba" = "CUB", "Switzerland" = "CHE",
  "Nicaragua" = "NIC", "Panama" = "PAN", "Belgium" = "BEL", "Egypt" = "EGY",
  "United Kingdom" = "GBR", "Greece" = "GRC", "Guatemala" = "GTM",
  "Syria" = "SYR", "Korea" = "KOR", "Netherlands" = "NLD",
  "Yugoslavia" = "YUG", "Pakistan" = "PAK", "Ireland" = "IRL",
  "Ecuador" = "ECU", "Israel" = "ISR", "Denmark" = "DNK",
  "Australia" = "AUS", "Mexico" = "MEX", "French Guiana" = "GUF",
  "Suriname" = "SUR", "Sweden" = "SWE", "Honduras" = "HND",
  "Canada" = "CAN", "El Salvador" = "SLV", "Finland" = "FIN",
  "Dominican Republic" = "DOM", "Bulgaria" = "BGR", "Norway" = "NOR"
)

```


## Carrega base 1991 (fonte: Centro de Estudos da Metrópole)

```{r base 1991 centro estudos metropole, comment=FALSE}
# transforma base sav em dta
# censo_1991_raw <- read_sav("E:/Thais/Tese_Mestrado/IBGE_1991/Censo 1991/censo_1991_25_percent.sav")
# censo_1991_raw$V0311 <- as.integer(censo_1991_raw$V0311)
# censo_1991_raw$V0322 <- as.integer(censo_1991_raw$V0322)
# censo_1991_raw$V3614 <- as.integer(censo_1991_raw$V3614)
# 
# df <- write_dta(censo_1991_raw, "E:/Thais/Tese_Mestrado/censo_1991/censo_1991_raw.dta")
# df <- read_dta("E:/Thais/Tese_Mestrado/censo_1991/censo_pessoas_1991_sem_comp.dta")
# write_parquet(df, "E:/Thais/Tese_Mestrado/censo_1991/censo_pessoas_1991_sem_comp.parquet")
# df <- read_parquet("E:/Thais/Tese_Mestrado/censo_1991/censo_pessoas_1991_sem_comp.parquet")

# df <- read_dta("E:/Thais/Tese_Mestrado/censo_1991/censo_pessoas_1991_filtrado_nao_comp.dta")
# 
# write_parquet(df, "E:/Thais/Tese_Mestrado/censo_1991/censo_pessoas_1991_filtrado_nao_comp.parquet")

df <- read_parquet("E:/Thais/Tese_Mestrado/censo_1991/censo_pessoas_1991_filtrado_nao_comp.parquet")

### Cultural proxies----

## Home country divorce rate
home_country_div_rate_1990 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/home_country_div_rate/home_country_div_rate_1990.xlsx")

### Country of Origin Variables, measured in the year 1991/1990 except where otherwise noted (paper)----

# ## GDP per capita
gdp_pc_1991 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/gdp_per_capita/gdp_pc_1991.xlsx")

## Average Female Age at First Marriage
mean_age_fmarr_1991 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/age_first_marriage/mean_age_fmarr_1991.xlsx")

## Total fertility rate
fertility_rate_1991 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/fertility_rate/fertility_rate_1991.xlsx")

## Remarriage rate

## Proportion: weekly  church attendance and catholics
church_catholic_1995_1998 <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/church/church_catholic_1995_1998.xlsx") |> 
  dplyr::mutate(pais_nascim = dplyr::recode(pais_nascim, !!!country_code_mapping))
  # dplyr::filter(pais_nascim %in% country_code_mapping)


##### ff2009 (idea)
## LFP 2000
#lfp <- read_xlsx("E:/Thais/Tese_Mestrado/tese_bases/lfp/lfp_final.xlsx")
```

## MANIPULAÇÕES

```{r manipula}
# Mantendo cópia das bases
cp1991_nc_copy <- df

# Renomeando países de origem
df <- df %>% rename(pais_nascim = V0316)
cp1991_nc_copy <- cp1991_nc_copy %>% rename(pais_nascim = V0316)

setDT(df, cp1991_nc_copy)


df <- cp1991_nc_copy %>%
  mutate(pais_nascim = case_when(
    pais_nascim == 30 ~ "ARG",
    pais_nascim == 31 ~ "BOL",
    pais_nascim == 32 ~ "CAN",
    pais_nascim == 33 ~ "CHL",
    pais_nascim == 34 ~ "COL",
    pais_nascim == 35 ~ "CRI",
    pais_nascim == 36 ~ "CUB",
    pais_nascim == 37 ~ "ECU",
    pais_nascim == 38 ~ "USA",
    pais_nascim == 39 ~ "GTM",
    pais_nascim == 40 ~ "GUY",
    pais_nascim == 41 ~ "GUF",
    pais_nascim == 42 ~ "HTI",
    pais_nascim == 43 ~ "HND",
    pais_nascim == 44 ~ "BLZ",
    pais_nascim == 45 ~ "JAM",
    pais_nascim == 46 ~ "MEX",
    pais_nascim == 47 ~ "NIC",
    pais_nascim == 48 ~ "PAN",
    pais_nascim == 49 ~ "PRY",
    pais_nascim == 50 ~ "PER",
    pais_nascim == 51 ~ "DOM",
    pais_nascim == 52 ~ "SLV",
    pais_nascim == 53 ~ "SUR",
    pais_nascim == 54 ~ "URY",
    pais_nascim == 55 ~ "VEN",
    pais_nascim == 56 ~ "OTH_AM",
    pais_nascim == 58 ~ "DEU",
    pais_nascim == 59 ~ "AUT",
    pais_nascim == 60 ~ "BEL",
    pais_nascim == 61 ~ "BGR",
    pais_nascim == 62 ~ "DNK",
    pais_nascim == 63 ~ "ESP",
    pais_nascim == 64 ~ "FIN",
    pais_nascim == 65 ~ "FRA",
    pais_nascim == 66 ~ "GBR",
    pais_nascim == 67 ~ "GRC",
    pais_nascim == 68 ~ "NLD",
    pais_nascim == 69 ~ "HUN",
    pais_nascim == 70 ~ "IRL",
    pais_nascim == 71 ~ "ITA",
    pais_nascim == 72 ~ "YUG",
    pais_nascim == 73 ~ "NOR",
    pais_nascim == 74 ~ "POL",
    pais_nascim == 75 ~ "PRT",
    pais_nascim == 76 ~ "ROU",
    pais_nascim == 77 ~ "SWE",
    pais_nascim == 78 ~ "CHE",
    pais_nascim == 79 ~ "CZE",
    pais_nascim == 80 ~ "RUS",
    pais_nascim == 81 ~ "OTH_EUR",
    pais_nascim == 82 ~ "AGO",
    pais_nascim == 83 ~ "EGY",
    pais_nascim == 84 ~ "MOZ",
    pais_nascim == 85 ~ "OTH_AFR",
    pais_nascim == 86 ~ "CHN",
    pais_nascim == 87 ~ "TWN",
    pais_nascim == 88 ~ "KOR",
    pais_nascim == 89 ~ "IND",
    pais_nascim == 90 ~ "ISR",
    pais_nascim == 91 ~ "JPN",
    pais_nascim == 92 ~ "LBN",
    pais_nascim == 93 ~ "PAK",
    pais_nascim == 94 ~ "SYR",
    pais_nascim == 95 ~ "TUR",
    pais_nascim == 96 ~ "OTH_ASIA",
    pais_nascim == 97 ~ "AUS",
    pais_nascim == 98 ~ "OTH_OCE",
    pais_nascim == 99 ~ "NO_SPEC",
    TRUE ~ as.character(pais_nascim)
  ))
```



```{r manipula 2}
# transform metropolitan area variable to a factor variable
df$V7003 <- as.factor(df$V7003)

df$ano <- 1991

df <- df %>%
  mutate(
    ano_nasc = ano - V3072,
    rm = ifelse(V7003 != 0, 1, 0), #metropolitan region
    imm = ifelse((V3152 - ano_nasc <= 5) & rm == 1, 1, 0),
    imm_div = ifelse(imm == 1
                     & V0333 == 7, 1, 0),
  )

df <- df %>% 
  filter(V3342 != 5) %>% #tira solteiros
  filter(V0333 != 8) %>% #tira viuvos
  filter(V0333 != 9) #tira nao declarado
  
# se imm_div e NA entao coloca zero
# df$imm_div[is.na(df$imm_div)] <- 0


df <- df %>%
  mutate(
    imm_homem = ifelse(V0301 == 1
                       & imm == 1, 1, 0),
    imm_alf = ifelse(imm == 1 & (V0323 == 1), 1, 0), 
    imm_fund_completo = ifelse(imm == 1
                               & (V0328 == 3 | V0328 == 4), 1, 0), 
    imm_em_completo = ifelse(imm == 1
                             & (V0328 == 5 | V0328 == 6), 1, 0), 
    imm_superior_completo = ifelse(imm == 1
                                   & (V0328 == 7), 1, 0), 
    imm_mestr_doc = ifelse(imm == 1
                           & (V0328 == 8), 1, 0),
    filho_mora_domicilio = ifelse(V0335 != 0, 1, 0),
    imm_mulher1filho = ifelse(imm == 1
                              & V0301 == 2
                              & (V3360 >= 1), 1, 0)
  )


df <- df |> rename(wage = V0356) #Rendimento Bruto da Ocupação Principal 

df <- df |> 
  mutate(
    annual_wage = wage * 12,
    log_wage = log(wage),
    wage_fem = ifelse(imm == 1 & V0301 == 2, wage * 12, 0), # annual salary for women, replace NA with 0
    log_wage_fem = log(ifelse(is.na(wage_fem), 0, wage_fem)), # replace NA with 0 before taking log
    wage_men = ifelse(imm == 1 & V0301 == 1, wage * 12, 0), # annual salary for men, replace NA with 0
    log_wage_men = log(ifelse(is.na(wage_men), 0, wage_men)) # replace NA with 0 before taking log
  )
```


```{r soma dados}
# numero de imigrantes na amostra
imm_base <- df %>% filter(imm == 1)
sum(imm_base$V7301)
```


```{r soma dados2}
# numero de imigrantes divorciados
imm_div_base <- df %>% filter(imm_div == 1)
sum(imm_div_base$V7301)
```
Somente na base de 1991 temos informação de filhos que moram com os pais, que é uma variável de controle importante.

```{r manipula2, comment=FALSE}
# Juntando as bases

# df com home country divorce rate
df <- merge(df, home_country_div_rate_1990, by = "pais_nascim", all.x = TRUE)
#----
# com gdp_pc: considerar ano 2000

df <- merge(df, gdp_pc_1991, by = "pais_nascim", all.x = TRUE)

# com age_f_first_marriage
df <- merge(df, mean_age_fmarr_1991, by = "pais_nascim", all.x = TRUE)

# com fertility_rate
df <- merge(df, fertility_rate_1991, by = "pais_nascim", all.x = TRUE)

# com fem lfp
# cp1991_nc_4 <- merge(cp1991_nc_3, lfp, by = "pais_nascim", all.x = TRUE)

# com church variables
## 1995_1998
df <- merge(df, church_catholic_1995_1998, by = "pais_nascim", all.x = TRUE)

# # com divorce never justifiable
# ## 1995_1998
# cp1991_nc_5 <- merge(cp1991_nc_4, church_catholic_1995_1998, by = "pais_nascim", all.x = TRUE)
# ## 1999_2004
# cp1991_nc_6 <- merge(cp1991_nc_5, church_catholic_1999_2004, by = "pais_nascim", all.x = TRUE)
# ## 2005_2009
# cp1991_nc_7 <- merge(cp1991_nc_6, church_catholic_2005_2009, by = "pais_nascim", all.x = TRUE)

# Tirando outros paises (...-others e paises com NA)----
df <- df %>% 
  filter(!`pais_nascim` %in% c("OTH_AFR", "OTH_AM", "OTH_ASIA","OTH_EUR", "OTH_OCE","NO_SPEC"))

df <- df %>% rename(escolaridade = V0328)
df$fund_completo <- ifelse((df$escolaridade == 3 | df$escolaridade == 4), 1, 0)
df$med_completo <- ifelse((df$escolaridade == 5 | df$escolaridade == 6), 1, 0)
df$sup_completo <- ifelse((df$escolaridade == 7 | df$escolaridade == 8), 1, 0)

# transforma escolaridade em continua
df$escolaridade_cont <- as.numeric(df$escolaridade)

# idade ao quadrado
df <- df %>%
  mutate(
    age_fem = if_else(V0301 == 2, V3072, NA_real_),
  ) %>%
  mutate(
    age_squared = V3072^2
  )
# 
# paises_para_remover <- c("AGO", "ARG", "BEL", "BGR", "BLZ", "BOL",    
#                          "CHN", "COL", "CRI", "CUB", "CZE", "DOM",    
#                          "ESP", "FIN", "GTM", "GUF", "GUY", "HND",    
#                          "HTI", "IND", "IRL", "ISR", "ITA", "JAM",    
#                          "LBN", "MOZ", "NIC", "NLD", "PAK",    
#                          "PER", "PRY", "SUR", "SYR", "TWN", "YUG")
# 
# # Filtrando o DataFrame para remover os países com NA em hcdr
# df <- df[!df$pais_nascim %in% paises_para_remover, ]
# 
# # Remove na coluna pais_nascim com valores NA
# df <- df[!is.na(df$pais_nascim), ]
# 
base_partial_nc_1991 <- as.data.frame(df)
# write_xlsx(base_partial_nc_1991, "E:/Thais/Tese_Mestrado/tese_bases/base_gerada/base_nc_1991.xlsx")

```

## Graph: number of immigrants on Census 
```{r number of immigrants total}
library(ggplot2)
country_counts <- df |>
  group_by(pais_nascim) |>
  summarize(total_weight = sum(V7301, na.rm = TRUE)) |>
  arrange(desc(total_weight))
colnames(country_counts) <- c("Country", "Count")

ggplot(country_counts, aes(x = reorder(Country, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +  
  labs(title = "Number of Observations by Country", 
       x = "Country", 
       y = "Number of Observations") +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 5.5),   
    axis.text.x = element_text(size = 7),   
    plot.title = element_text(size = 7, hjust = 0.5), 
    plot.margin = margin(1, 1, 1, 1, "cm")  
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.03)))
```
## Graph: number of immigrants on Census with hcdr !=0
```{r number of immigrants with hcdr}
library(ggplot2)

country_counts_hcdr <- df |>
  filter(hcdr != 0) |>  
  group_by(pais_nascim) |>
  summarize(total_weight = sum(V7301, na.rm = TRUE)) |>
  arrange(desc(total_weight))

colnames(country_counts_hcdr) <- c("Country", "Count")

ggplot(country_counts_hcdr, aes(x = reorder(Country, Count), y = Count)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  coord_flip() +  
  labs(title = "Number of Observations by Country", 
       x = "Country", 
       y = "Number of Observations") +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 5.5),   
    axis.text.x = element_text(size = 7),   
    plot.title = element_text(size = 7, hjust = 0.5), 
    plot.margin = margin(1, 1, 1, 1, "cm")  
  ) +
  scale_y_continuous(expand = expansion(mult = c(0, 0.03)))
```

## FE Regressions
```{r reg1}
## Rodando a regressao (1) - table 2
# FE: idade e escolaridade
model1_nc <- feols(imm_div ~ hcdr + imm_homem + imm_fund_completo + imm_em_completo + imm_superior_completo | factor(V3072) + age_squared, data = base_partial_nc_1991, weights = ~V7301, cluster = ~pais_nascim)
summary(model1_nc)
```

```{r reg2}
# FE: idade com escolaridade continua
model1_1_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont | factor(V3072) + age_squared, data = base_partial_nc_1991, weights = ~V7301, cluster = ~pais_nascim)
summary(model1_1_nc)
```


```{r reg3}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont | factor(V3072) +age_squared + V7003, data = base_partial_nc_1991, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc)
```

```{r quantos imigrantes de portugual?}
base_partial_nc_portugal <- base_partial_nc_1991 %>%
  filter(pais_nascim == "PRT")

base_partial_nc_portugal <- base_partial_nc_portugal %>% filter(imm == 1)
sum(base_partial_nc_portugal$V7301)
```


```{r reg4}
# Drop Portugal (3): maior numero de imigrantes
base_partial_nc_sem_portugal <- base_partial_nc_1991 %>%
  filter(pais_nascim != "PRT")
model2_nc_sem_portugal <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont | factor(V3072) + age_squared + V7003, data = base_partial_nc_sem_portugal, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc_sem_portugal)
```
Resultados se aproximam do paper quando tiramos Portugal, que é um outlier em termos de imigrantes.

```{r quantos imigrantes da russia?}
base_partial_nc_russia <- base_partial_nc_1991 %>%
  filter(pais_nascim == "RUS")

base_partial_nc_russia <- base_partial_nc_russia %>% filter(imm == 1)
sum(base_partial_nc_russia$V7301)
```

```{r reg5}
# Drop Russia (and Italy) (4)
base_partial_nc_sem_russia_italy <- base_partial_nc_1991 %>%
  filter(pais_nascim != "RUS")

model2_nc_sem_russia_italy <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont | V3072+age_squared+V7003, data = base_partial_nc_sem_russia_italy, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc_sem_russia_italy)

```
Resultado não se mantém quando tiramos a Russia.

```{r quantos imigrantes da italia?}
# ainda nao tenho informacao da italia pros anos 1990
# base_partial_nc_sem_italia <- base_partial_nc_1991 %>%
#   filter(pais_nascim != "PRT")
# 
# base_partial_nc_sem_italia <- base_partial_nc_sem_italia %>% filter(imm == 1)
# sum(base_partial_nc_sem_italia$V7301)
```

# Split sample
We also separate the analysis by gender to test the hypothesis that women are more sensitive to divorce culture than men p.1016

## Women
### With hcdr

```{r w1}
# Split sample: women
base_partial_nc_women <- df |>
  filter(V0301 == 2)

model2_nc_women4 <- feols(imm_div ~ hcdr, data = base_partial_nc_women, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc_women4)
```
### With age dummy variables and msa fixed effects
```{r w2}
model2_nc_women5 <- feols(imm_div ~ hcdr + imm_homem + imm_fund_completo + imm_em_completo + imm_superior_completo | factor(V3072) + age_squared + V7003, data = base_partial_nc_women, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc_women5)
```

### Plus children that live in the hh

```{r w3}
model2_nc_women6 <- feols(imm_div ~ hcdr + imm_homem + imm_fund_completo + imm_em_completo + imm_superior_completo + filho_mora_domicilio| factor(V3072) + age_squared + V7003, data = base_partial_nc_women, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc_women6)
```
### Plus log(annual wage income) and age_children < 18
```{r w4}
model2_nc_women7<- feols(imm_div ~ hcdr + imm_homem + imm_fund_completo + imm_em_completo + imm_superior_completo + filho_mora_domicilio + log_wage_fem| factor(V3072) + age_squared + V7003, data = base_partial_nc_women, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc_women7)
```

## Men
### With hcdr

```{r m1}
# Split sample: men
base_partial_nc_men <- df |>
  filter(V0301 == 1)

model2_nc_men1 <- feols(imm_div ~ hcdr, data = base_partial_nc_men, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc_men1)

```
## Table 3: Home-country differences and the probability of being currently divorced (p.1026)
### with gdp_pc

```{r 3.1}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont + gdp_pc_in_100000| factor(V3072)+age_squared+V7003, data = df, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc)

```
### with country-of-origin fertility rate
```{r}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont + fertility_rate| factor(V3072)+age_squared+V7003, data = df, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc)
```

## with Average female age at first marriage
```{r ffm}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr + imm_homem + escolaridade_cont + ffm| factor(V3072)+age_squared+V7003, data = df, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc)

```

### with Everything! (not endogamy rate)
```{r everything}
# FE: idade e RM
model2_nc <- feols(imm_div ~ hcdr +
                     imm_homem +
                     escolaridade_cont +
                     gdp_pc_in_100000 +
                     fertility_rate +
                     tx_once_week_church_1995_1998 +
                     tx_catholic_1995_1998 +
                     ffm |
                     factor(V3072)+age_squared+V7003, data = df, weights = ~V7301, cluster = ~pais_nascim)
summary(model2_nc)

```

